\pkg{cubble}: An \proglang{R} Package for Organizing and Wrangling Multivariate Spatio-temporal Data

### 2023-05-29 4-3-matching.Rmd
rename files

```{r}
load(here::here("data/climate_full.rda"))

@@

river <- river |> mutate(type = "river")
```

@@

```{r echo = TRUE}
res <- match_sites(
  river, climate,
  temporal_by = c("Water_course_level" = "prcp"),
  temporal_independent = "prcp",  
  temporal_n_highest = 30,
  temporal_min_match = 15, 
)
```

@@

```{r}
res |> print()
```

@@

```{r matching, out.width="100%", fig.height = 5, fig.width = 10, fig.cap="Weather stations and river gauges with matched pairs labelled on the map (a) and plotted across time (b). Precipitation and water level have been standardised between 0 and 1 to be displayed on the same scale. The water level reflects the increase in precipitation. The numbers (1, 5, 6, 10) indicate the group index derived from spatial matching, only those that were selectd by temporal matching are shown here."}
vic_map <- ozmaps::abs_ste |> 
  filter(NAME == "Victoria") |> 
  rmapshaper::ms_simplify()

>>>>

```{r}

load(here::here("data/climate_full.rda"))

@@

river <- cubble::river %>% unnest(ts) %>% as_cubble(key = station, index = date, coords = c(long, lat)) |> mutate(type = "river")
```

@@

```{r echo = TRUE, eval = FALSE}
res <- match_sites(
  river, climate,
  temporal_by = c("Water_course_level" = "prcp"),
  temporal_independent = "prcp",  
  temporal_n_highest = 30,
  temporal_min_match = 15, 
)
```

@@

```{r eval = FALSE}
res |> print()
```

@@

```{r matching, eval = FALSE, out.width="100%", fig.height = 5, fig.width = 10, fig.cap="Weather stations and river gauges with matched pairs labelled on the map (a) and plotted across time (b). Precipitation and water level have been standardised between 0 and 1 to be displayed on the same scale. The water level reflects the increase in precipitation. The numbers (1, 5, 6, 10) indicate the group index derived from spatial matching, only those that were selectd by temporal matching are shown here."}
vic_map <- ozmaps::abs_ste |> 
  filter(NAME == "Victoria") |> 
  rmapshaper::ms_simplify()

### 2023-05-29 jss/main.tex
rename files

\begin{CodeChunk}
\begin{CodeInput}
R> make_cubble(
+   spatial = stations_sf, temporal = meteo, key = id, index = date
+   )
R> 
R> make_cubble(
+   spatial = stations, temporal = meteo_ts, coords = c(long, lat)
+   )
R> 
R> make_cubble(spatial = stations_sf, temporal = meteo_ts)
\end{CodeInput}
\end{CodeChunk}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> cb_back <- cb_long |> face_spatial()
R> cb_back
\end{CodeInput}
\begin{CodeOutput}
# cubble:   key: id [3], index: date, nested form
# extent:   [144.8321, -37.98, 145.0964, -37.6655]
# temporal: prcp [dbl], tmax [dbl], tmin [dbl]
  id           long   lat  elev name              wmo_id ts      
  <chr>       <dbl> <dbl> <dbl> <chr>              <dbl> <list>  
1 ASN00086038  145. -37.7  78.4 essendon airport   95866 <tibble>
2 ASN00086077  145. -38.0  12.1 moorabbin airport  94870 <tibble>
3 ASN00086282  145. -37.7 113.  melbourne airport  94866 <tibble>
\end{CodeOutput}
\begin{CodeInput}
R> identical(cb_nested, cb_back)
\end{CodeInput}
\begin{CodeOutput}
[1] FALSE
\end{CodeOutput}
\end{CodeChunk}

>>>>

\begin{CodeChunk}
\begin{CodeInput}
R> make_cubble(spatial = stations_sf, temporal = meteo, 
+             key = id, index = date)
R> 
R> make_cubble(spatial = stations, temporal = meteo_ts, 
+             coords = c(long, lat))
R> 
R> make_cubble(spatial = stations_sf, temporal = meteo_ts)
\end{CodeInput}
\end{CodeChunk}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> (cb_back <- cb_long |> face_spatial())
\end{CodeInput}
\begin{CodeOutput}
# cubble:   key: id [3], index: date, nested form
# extent:   [144.8321, -37.98, 145.0964, -37.6655]
# temporal: prcp [dbl], tmax [dbl], tmin [dbl]
  id           long   lat  elev name              wmo_id ts      
  <chr>       <dbl> <dbl> <dbl> <chr>              <dbl> <list>  
1 ASN00086038  145. -37.7  78.4 essendon airport   95866 <tibble>
2 ASN00086077  145. -38.0  12.1 moorabbin airport  94870 <tibble>
3 ASN00086282  145. -37.7 113.  melbourne airport  94866 <tibble>
\end{CodeOutput}
\begin{CodeInput}
R> #identical(cb_nested, cb_back)
\end{CodeInput}
\end{CodeChunk}
